Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-23 paper/paper.qmd
results updated

>>>>

Upon assessing the generated datasets from Project Gutenberg, we further extrapolate on them here by combining word count with the AFINN, Bing and NRC index to conduct relevant word frequency and sentiment analysis. The later sections of Results also compound on these findings to conduct a comparative analysis between gendered and transnational SOC authors, attempting to garner relevant insights in mental health themes in different demographics of the SOC genre.
